---
title: "CRP_Oddball_Modulation"
author: "Peris-Yague et al. 2021"
date: "8/17/2021"
output: 
  github_document:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r  echo=FALSE, results='hide', message=FALSE, warning=FALSE}
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)

#Install all libraries 

library(tidyverse)
library(ggpubr)
library(rstatix)
library(rsample)
library(dplyr)
library(ggplot2)
library(data.table)
library(effects)
library(lme4)
library(plyr)
library(emmeans)
```


# Fig. 1C Relative Recall Position by SOA 


```{r echo=FALSE, warning=FALSE, message=FALSE} 
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
RR<-read.csv('RR.csv')
RR<-as.data.frame(RR)
#head(RR) #to show you what my raw data looks like 
RR$oddballtype<-factor(RR$oddballtype)
RR$SOA<-factor(RR$SOA)
RR$subject<-factor(RR$subject)

RR.plot.SOA.data<- RR %>%
  group_by(SOA, oddballtype) %>%
  get_summary_stats(relativerecall, type='mean_ci')

#calculate mean for emotional and perceptual
mean.calc<- RR %>%
  group_by(oddballtype) %>%
  get_summary_stats(relativerecall,type='mean_ci')
  

RR.SOA.plt2<-ggplot(RR.plot.SOA.data, aes(x=SOA,y=mean, group=oddballtype, shape=oddballtype, color=SOA, ymin=mean-ci, ymax=mean+ci))+ 
  geom_pointrange(position=position_dodge(width=0.5), size=1)+
  scale_color_brewer(palette='Set2')+
  theme_classic()+
  theme(strip.background=element_blank(), text=element_text(size=17))+
  xlab('Stimulus Onset Asynchrony')+
  ylab('Relative Recall Position')+
  labs(color='SOA', shape='Oddball Type')+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))

RR.SOA.plt2

#Now let's run a 2-way ANOVA with oddball x SOA as factors on relative recall 

#Check normality with QQ plots
RR.SOA.QQ<-ggqqplot(RR,'relativerecall',ggtheme=theme_bw())+
  facet_grid(oddballtype~SOA, labeller='label_both')
#RR.SOA.QQ #doesn't look normal
#hist(RR$relativerecall)
#lines(density(RR$relativerecall))

#Check homogeneity of variances
leveneRR<-levene_test(relativerecall ~ oddballtype*SOA, data=RR)
#leveneRR # homogeneity of variances is violated


#The assumption of sphericity is violated in the dataset doing a trial by trial analyses. However, data is normally distributed if averaging accross SOAs per subject. 

RR.avg<-read.csv('RR_average.csv')
RR.avg<-as.data.frame(RR.avg)
RR.avg$oddballtype<-factor(RR.avg$oddballtype)
RR.avg$SOA<-factor(RR.avg$SOA)
RR.avg$subject<-factor(RR.avg$subject)

RR.avg.levene<-levene_test(relativerecall ~ oddballtype*SOA, data=RR.avg) #this is ok 
RR.avg.QQ<-ggqqplot(RR.avg,'relativerecall',ggtheme=theme_bw())+
  facet_grid(oddballtype~SOA, labeller='label_both')
#RR.avg.QQ #looks roughly ok 

RR.aov<-anova_test(
  data=RR.avg,dv=relativerecall,wid=subject, 
  within=c(SOA,oddballtype),
)

#get_anova_table(RR.aov)

#DF are wrong because of missing values. Re-calculated with Prism. 


```


# Fig. 1D Amount of items recalled per SOA

```{r echo=FALSE,warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")

listrecallSOA<-read.csv('list_recall_SOA_R.csv')
listrecallSOA<-as.data.frame(listrecallSOA)
listrecallSOA$SOA<-factor(listrecallSOA$SOA)
listrecallSOA$subject<-factor(listrecallSOA$subject)

listrecallSOAplot<-listrecallSOA %>%
  group_by(SOA) %>%
  get_summary_stats(total_recall_list,type='mean_ci')

# Plot 
list.recall.SOA.fig2<-ggplot(data=listrecallSOAplot, aes(x=as.factor(SOA), y=mean, color=SOA, min=mean-ci, ymax=mean+ci))+
  geom_pointrange(position=position_dodge(width=0.5), shape=15, size=1)+
  scale_color_brewer(palette="Set2")+
  scale_y_continuous(n.breaks=10)+
  theme_classic()+
  labs(x='Stimulus Onset Asynchrony', y='Average amount of items recalled')+
  theme(text=element_text(size=17))+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))

list.recall.SOA.fig2

listrecallSOA.data<- listrecallSOA %>%
  group_by(SOA,subject) %>%
  get_summary_stats(total_recall_list, type='mean')

listrecallSOA.data<-listrecallSOA.data[-c(3,4)]
names(listrecallSOA.data)[3] <- "total_recall_list"

listrecallSOA.data<-as.data.frame(listrecallSOA.data)
listrecallSOA.data$SOA<-as.factor(listrecallSOA.data$SOA)
listrecallSOA.data$subject<-as.factor(listrecallSOA.data$subject)
listrecallSOA.data$total_recall_list<-as.numeric(listrecallSOA.data$total_recall_list)

#Check normal distribution 
list.recall.SOA.QQ<-ggqqplot(listrecallSOA.data,'total_recall_list',ggtheme=theme_bw())+
  facet_grid(~SOA, labeller='label_both') 

#list.recall.SOA.QQ# looks fine 

# Run an ANOVA
listrecallSOA.aov<-anova_test(
  data=listrecallSOA.data,dv=total_recall_list,wid=subject, 
  within=c(SOA),
)

get_anova_table(listrecallSOA.aov)
  
listrecallSOA.wide<-reshape(listrecallSOA, idvar = 'subject', timevar = 'SOA', direction = 'wide')
names(listrecallSOA.wide)[2] <- "SOA 6"
names(listrecallSOA.wide)[3] <- "SOA 3"
names(listrecallSOA.wide)[4] <- "SOA 2"
names(listrecallSOA.wide)[5] <- "SOA 1"
names(listrecallSOA.wide)[6] <- "SOA 4"


path_out<-'/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results/'
write.csv(listrecallSOA.wide,paste(path_out,'Fig1D_prism.csv',sep = ''))

```


# Fig. 2A Conditional Response Probability Curves


```{r echo=FALSE,warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
CRPall<-read.csv('CRP_all_R.csv')
CRPall<-as.data.frame(CRPall)

crpplot<-CRPall %>%
  group_by(oddballtype,wordposition, direction) %>%
  get_summary_stats(CRP,type='mean_se')

## This is needed to make the 'backwards' lags negative so that they plot
# correctly 
wpplot<-numeric(0)
for (rows in 1:nrow(crpplot)){
  if (crpplot$direction[rows] == "Backwards") {
    wpplot[rows]<-(crpplot$wordposition[rows])*-1
  }
  else {wpplot[rows]<-(crpplot$wordposition[rows])
  }
}
invisible(as.data.frame(wpplot))
crpplot$wpplot<-wpplot

pltCRP<-ggplot(crpplot,aes(x=wpplot,y=mean), group=oddballtype)+
        geom_line(aes(color=oddballtype), size=1) +
        geom_point(aes(color=oddballtype), size=2) +
        theme_classic()+
        facet_wrap(~ direction, scales='free_x', ncol=2)+    
        theme(strip.background = element_blank())+
        theme(text=element_text(size=17))+
        #ggtitle('CRP all')+
        xlab('Lag') +
        ylab('Conditional Response Probability')+
        scale_color_manual(values=c('violetred2','turquoise2'), 
          labels=c('Emotional','Perceptual'), name='Oddball List Type')+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))
                    
pltCRP

CRPall$subject<-factor(CRPall$subject)
CRPall$oddballtype<-factor(CRPall$oddballtype)
CRPall$direction<-factor(CRPall$direction)
CRPall$wordposition<-factor(CRPall$wordposition)

#Check for normality and homogeneity of variances 

CRP.QQ<-ggqqplot(CRPall,'CRP',ggtheme=theme_bw())+
  facet_grid(oddballtype+direction~wordposition, labeller='label_both') 

#CRP.QQ # looks fine 

#If homogeneity of variances is violated, sphericity is automatically corrected in get_anova_table with Greenhouse-Geisser correction. 

#Run RM ANOVA
CRPall.aov<-anova_test(
  data=CRPall,dv=CRP,wid=subject,
  within=c(oddballtype,wordposition,direction)
)
#CRPall.aov
get_anova_table(CRPall.aov)

#Interaction word position x direction 

WpxDir.data<-aggregate(x = CRPall$CRP, by = list(wordposition=CRPall$wordposition, direction=CRPall$direction, subject=CRPall$subject), FUN = "mean")

WpxDir.pwc1<- WpxDir.data %>%
  group_by(direction) %>%
  pairwise_t_test(x~wordposition,paired=TRUE, p.adjust.method='fdr')
WpxDir.pwc1

WpxDir.data %>%
  group_by(direction) %>%
  cohens_d(x~wordposition, paired=TRUE)

WpxDir.pwc2<- WpxDir.data %>%
  group_by(wordposition) %>%
  pairwise_t_test(x~direction,paired=TRUE, p.adjust.method='fdr')
WpxDir.pwc2

WpxDir.data %>%
  group_by(wordposition) %>%
  cohens_d(x~direction, paired=TRUE)




```



# Fig. 2B Conditional Response Probability Curves by Stimulus Onset Asynchrony

```{r echo=FALSE, warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
CRPSOA<-read.csv('all_CRP_SOA_R.csv')
CRPSOA<-as.data.frame(CRPSOA)

CRPSOAplot<-CRPSOA %>%
  group_by(wordposition, direction, SOA) %>%
  get_summary_stats(CRP,type='mean_se')

wpplot<-numeric(0)
for (rows in 1:nrow(CRPSOAplot)){
  if (CRPSOAplot$direction[rows] == "Backwards") {
    wpplot[rows]<-(CRPSOAplot$wordposition[rows])*-1
  }
  else {wpplot[rows]<-(CRPSOAplot$wordposition[rows])
  }
}
invisible(as.data.frame(wpplot))
CRPSOAplot$wpplot<-wpplot

#factor all the categorical variables 
CRPSOA$SOA<-factor(CRPSOA$SOA)
CRPSOA$direction<-factor(CRPSOA$direction)
CRPSOA$wordposition<-factor(CRPSOA$wordposition)
CRPSOA$subject<-factor(CRPSOA$subject)
CRPSOA$oddballtype<-factor(CRPSOA$oddballtype)

pltCRPSOA<-ggplot(CRPSOAplot,aes(x=wpplot,y=mean, group=SOA, color=as.factor(SOA)))+
  geom_line(size=1) +
  geom_point(size=2) +
  theme_classic()+
  facet_wrap(~ direction, scales='free_x', ncol=2)+ 
  theme(strip.background = element_blank())+
  theme(text=element_text(size=17))+
  xlab('Lag') +
  ylab('Conditional Response Probability')+
  scale_color_brewer(palette="Set2")+
  labs(color='SOA')+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))

pltCRPSOA

CRP.SOA.data<-aggregate(x = CRPSOA$CRP, by = list(SOA=CRPSOA$SOA, direction=CRPSOA$direction, subject=CRPSOA$subject), FUN = "mean")

#subset data only in the forwards direction 
CRP.SOA.data<-as.data.frame(subset(CRP.SOA.data, direction=='Forwards'))

CRP.SOA.QQ<-ggqqplot(CRP.SOA.data,'x',ggtheme=theme_bw())+
  facet_grid(~SOA, labeller='label_both') 

#Run a one-way ANOVA
CRPall.SOA.aov<-anova_test(
  data=CRP.SOA.data,dv=x,wid=subject,
  within=c(SOA)
)
#CRPall.SOA.aov
get_anova_table(CRPall.SOA.aov)

#Run follow-up t-tests 
SOA.pwc<- CRP.SOA.data %>%
  pairwise_t_test(x~SOA,paired=TRUE, p.adjust.method='fdr')
SOA.pwc

CRP.SOA.data %>%
  cohens_d(x~SOA, paired=TRUE)


#Run a Friedman test on JASP 
#CRPSOA.grouped<-CRPSOA %>%
 # group_by(subject, SOA, direction, wordposition) %>%
  #get_summary_stats(CRP,type='mean_se')

#CRPSOA.grouped<-CRPSOA.grouped[,c('subject','SOA','direction','wordposition','mean')]
#CRPSOA.grouped<-as.data.frame(CRPSOA.grouped)

#CRP.SOA.QQ<-ggqqplot(CRPSOA.grouped,'mean',ggtheme=theme_bw())+
 # facet_grid(direction+wordposition~SOA, labeller='label_both') 

#names(CRPSOA.grouped)[5] <- "CRP"

#CRPall.SOA.aov<-anova_test(
#  data=CRPSOA.grouped,dv=CRP,wid=subject,
#  within=c(SOA,wordposition,direction)
#)
#CRPall.SOA.aov
#get_anova_table(CRPall.SOA.aov)

#Follow-up the 3 Way interaction 
#SOAxWpxDir<-CRPSOA.grouped %>%
#  group_by(SOA) %>%
#  anova_test(dv=CRP, wid=subject, within = c(wordposition,direction))

#path_out<-'/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results/'
#write.csv(CRPSOA.grouped,paste(path_out,'Fig2B_jasp.csv',sep = ''))

  
```


# Fig. 3C Conditional Response Probability Curves transitions ***to*** and ***from*** oddballs

```{r echo=FALSE, warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
TFCRP<-read.csv('ToFrom_CRP_R.csv')
TFCRP<-as.data.frame(TFCRP)
#head(TFCRP) #to show you what my raw data looks like 

TFplot<-TFCRP %>%
  group_by(oddballtype,wordposition, direction,transition) %>%
  get_summary_stats(CRP,type='mean_se')

wpplot<-numeric(0)
for (rows in 1:nrow(TFplot)){
  if (TFplot$direction[rows] == "Backwards") {
    wpplot[rows]<-(TFplot$wordposition[rows])*-1
  }
  else {wpplot[rows]<-(TFplot$wordposition[rows])
  }
}
invisible(as.data.frame(wpplot))
TFplot$wpplot<-wpplot
TFplot$transition<-factor(TFplot$transition, levels=c('to','from'))

transition.labs<- c('Transition TO the oddball', 'Transition FROM the oddball')
names(transition.labs)<-c('to', 'from')


pltTF<-ggplot(TFplot,aes(x=wpplot,y=mean), group=oddballtype)+
  geom_line(aes(color=oddballtype), size=1) +
  geom_point(aes(color=oddballtype), size=2) +
   theme_classic()+
  facet_grid(transition~direction, scales='free_x', 
             labeller=labeller(transition = as_labeller(transition.labs)))+   
  theme(strip.background = element_blank())+
  theme(text=element_text(size=17))+
  #ggtitle('CRP transitions to and from the oddballs')+
  xlab('Lag') +
  ylab('Conditional Response Probability')+
  scale_color_manual(values=c('violetred2','turquoise2'), 
                     labels=c('Emotional','Perceptual'), name='Oddball List Type')+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))
 

pltTF

TFCRP$subject<-factor(TFCRP$subject)
TFCRP$oddballtype<-factor(TFCRP$oddballtype)
TFCRP$transition<-factor(TFCRP$transition)
TFCRP$direction<-factor(TFCRP$direction)
TFCRP$wordposition<-factor(TFCRP$wordposition)

#Collapsing accross lags 'omitnan'
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
TFCRP_collapsed<-read.csv('collapsed_CRP_omitnan.csv')
TFCRP_collapsed<-as.data.frame(TFCRP_collapsed)

TF.QQ<-ggqqplot(TFCRP_collapsed,'CRPmean',ggtheme=theme_bw())+
  facet_grid(oddballtype+direction~transition, labeller='label_both') 
#TF.QQ # QQ plots look fine 

levene.TF<-levene_test(CRPmean ~ oddballtype*direction*transition, data=TFCRP_collapsed)
#levene.TF #assumption violated, however, this doesn't apply to our data because we have only 2 levels for each IV (factor)

TFCRP_collapsed$subject<-as.factor(TFCRP_collapsed$subject)
TFCRP_collapsed$oddballtype<-as.factor(TFCRP_collapsed$oddballtype)
TFCRP_collapsed$transition<-as.factor(TFCRP_collapsed$transition)
TFCRP_collapsed$direction<-as.factor(TFCRP_collapsed$direction)


TF.collapsed.aov<-anova_test(
  data=TFCRP_collapsed,dv=CRPmean,wid=subject, 
  within=c(oddballtype,direction,transition),
)
get_anova_table(TF.collapsed.aov)

#Oddballtype x transition interaction 
OddxTr.data<-aggregate(x = TFCRP_collapsed$CRPmean, by = list(transition=TFCRP_collapsed$transition, oddballtype=TFCRP_collapsed$oddballtype, subject=TFCRP_collapsed$subject), FUN = "mean")

OddxTr.pwc<- OddxTr.data %>%
  group_by(oddballtype) %>%
  pairwise_t_test(x~transition, paired=TRUE, p.adjust.method = 'fdr')
OddxTr.pwc

OddxTr.data %>%
  group_by(oddballtype) %>%
  cohens_d(x~transition, paired=TRUE)

#Direction x transition interaction 
DirxTr.data<-aggregate(x = TFCRP_collapsed$CRPmean, by = list(transition=TFCRP_collapsed$transition, direction=TFCRP_collapsed$direction, subject=TFCRP_collapsed$subject), FUN = "mean")

DirxTr.pwc<- DirxTr.data %>%
  group_by(direction) %>%
  pairwise_t_test(x~transition, paired=TRUE, p.adjust.method = 'fdr')
DirxTr.pwc

DirxTr.data %>%
  group_by(direction) %>%
  cohens_d(x~transition, paired=TRUE)


#Plot 2 
transition.labs<- c('Transition TO the oddball', 'Transition FROM the oddball')
names(transition.labs)<-c('to', 'from')

neworder <- c("to","from")
TFCRP_collapsed.neworder <- arrange(transform(TFCRP_collapsed,
             transition=factor(transition,levels=neworder)),transition)

pltTF.collapsed<-ggplot(TFCRP_collapsed,aes(x=direction,y=CRPmean), group=oddballtype)+
  geom_boxplot(aes(color=oddballtype)) +
   theme_classic()+
  facet_grid(~transition, scales='free_x', 
             labeller=labeller(transition = as_labeller(transition.labs)))+   
  theme(text=element_text(size=17))+
  theme(strip.background = element_blank())+
  xlab('Collapsed Lag') +
  ylab('Conditional Response Probability')+
  scale_color_manual(values=c('violetred2','turquoise2'), 
                     labels=c('Emotional','Perceptual'), name='Oddball Type')

#pltTF.collapsed

```
# Fig. 4 Condutional Response Probability Curves by SOA transitions ***to*** and ***from*** oddballs


```{r echo=FALSE, warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
data_collapsed<-read.csv('E_lag_collapsed_R.csv')
data_collapsed<-as.data.frame(data_collapsed)

data_collapsed$subject<-factor(data_collapsed$subject)
data_collapsed$SOA<-factor(data_collapsed$SOA)
data_collapsed$transition<-factor(data_collapsed$transition)
data_collapsed$direction<-factor(data_collapsed$direction)

### Plot data ###
plot3w <-data_collapsed %>%
  group_by(direction, transition,SOA) %>%
  get_summary_stats(CRPmean,type='mean_ci')#%>%

neworder <- c("to","from")
plot3w.order <- arrange(transform(plot3w,
             transition=factor(transition,levels=neworder)),transition)

CRPSOA.plt<-ggplot(plot3w.order, aes(x=SOA,y=mean, group=direction, shape=direction, color=SOA,  ymin=mean-ci, ymax=mean+ci))+ 
geom_pointrange(position=position_dodge(width=0.5), size=1)+
  scale_shape_manual(values=c(1, 16))+
  facet_grid(~transition)+
  scale_color_brewer(palette="Set2")+
  labs(color='SOA')+
  ylab('Conditional Response Probability')+
  xlab('Stimulus Onset Asynchrony')+
  theme_classic()+
  theme(text=element_text(size=17))+
  theme(strip.background = element_blank())+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))

CRPSOA.plt


#Check Normality 
TF.SOA.QQ<-ggqqplot(data_collapsed,'CRPmean',ggtheme=theme_bw())+
  facet_grid(direction+transition~SOA, labeller='label_both') 
#TF.SOA.QQ #not normally distributed 
#hist(data_collapsed$CRPmean)

levene.TF.SOA<-levene_test(CRPmean ~ direction*transition*SOA, data=data_collapsed)
#levene.TF.SOA #assumption violated 

#Run separate non parametric tests
TovFrom.CRP.SOA <- data_collapsed %>%
  group_by(transition, subject) %>%
  get_summary_stats(CRPmean,type='mean_ci')


TovFrom.wilcox<- TovFrom.CRP.SOA %>%
  wilcox_test(mean~transition, paired=TRUE) 
TovFrom.wilcox

TovFrom.wilcox.effsize<- TovFrom.CRP.SOA %>%
  wilcox_effsize(mean~transition, paired=TRUE) 
TovFrom.wilcox.effsize

#check which mean is larger 
#data_collapsed %>%
#  group_by(transition) %>%
#  get_summary_stats(CRPmean,type='mean_ci')

path_out<-'/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results/'
write.csv(TovFrom.CRP.SOA,paste(path_out,'Fig4_intext_prism.csv',sep = ''))


#stats to assess whether transitions from emotional oddballs at SOA 1 were different than the others. 

BvF.from.SOA<- data_collapsed %>%
  group_by(direction, SOA, subject, transition) %>%
  get_summary_stats(CRPmean, type='mean_ci')

BvF.from.SOA<-as.data.frame(subset(BvF.from.SOA, transition=='from'))


#subset data in the forwards direction 
F.from.SOA<-as.data.frame(subset(BvF.from.SOA, direction=='forwards'))

F.from.SOA.wide<-reshape(F.from.SOA, idvar = "subject", timevar = "SOA", direction = "wide")
F.from.SOA.wide<-F.from.SOA.wide[,c('subject','mean.1','mean.2','mean.3','mean.4','mean.6')] #contains subject, SOA is each column and CRP mean inside


#rename the columns 
names(F.from.SOA.wide)[2] <- "1"
names(F.from.SOA.wide)[3] <- "2"
names(F.from.SOA.wide)[4] <- "3"
names(F.from.SOA.wide)[5] <- "4"
names(F.from.SOA.wide)[6] <- "6"

#save data to run the Friedman test on Prism 
path_out<-'/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results/'
write.csv(F.from.SOA.wide,paste(path_out,'Fig4_Forward_from_SOA_jasp.csv',sep = ''))



```





# ***Supplementary Material Analyses***

# Fig. S1 Conditional Response Probability Curves in remembered vs. forgotten oddballs 

```{r echo=FALSE,warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
RvF<-read.csv('rvf_CRP_R.csv')
RvF<-as.data.frame(RvF)
#head(RvF) #to show you what my raw data looks like 

rvfplot<-RvF %>%
  group_by(oddballtype,wordposition, direction,recall) %>%
  get_summary_stats(CRP,type='mean_se')

wpplot<-numeric(0)
for (rows in 1:nrow(rvfplot)){
  if (rvfplot$direction[rows] == "Backwards") {
    wpplot[rows]<-(rvfplot$wordposition[rows])*-1
  }
  else {wpplot[rows]<-(rvfplot$wordposition[rows])
  }
}
invisible(as.data.frame(wpplot))
rvfplot$wpplot<-wpplot

pltRVF<-ggplot(rvfplot,aes(x=wpplot,y=mean), group=oddballtype)+
  geom_line(aes(color=oddballtype)) +
  geom_point(aes(color=oddballtype)) +
  facet_wrap(~ recall + direction, scales='free_x')+   
  #ggtitle('CRP forgotten vs. recalled oddballs')+
  xlab('Lag') +
  ylab('Conditional Response Probability')+
  scale_color_manual(values=c('violetred2','turquoise2'), 
                     labels=c('Emotional','Perceptual'), name='Oddball List Type')+
  theme_classic()
pltRVF


```


# Fig. S2 Normalized Recall 

```{r echo=FALSE,warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
recall<-read.csv('normrec_R.csv')
recall<-as.data.frame(recall)

recall$subject<-factor(recall$subject)
recall$oddballtype<-factor(recall$oddballtype)
recall$wordposition<-factor(recall$wordposition)

recallplot<-recall %>%
  group_by(oddballtype,wordposition) %>%
  get_summary_stats(normrec,type='mean_ci')
recallplot <- dplyr::rename(recallplot, c('normrec' = mean))

recall.fig<-ggplot(recallplot, aes(fill=oddballtype, x=wordposition, y=normrec))+
  geom_bar(position='dodge', stat='identity')+
  geom_errorbar(aes(x=wordposition, ymin=normrec-ci, ymax=normrec+ci), width=0.4, color='wheat4',
                size=0.5, position=position_dodge(0.9), stat='identity')+ 
  geom_jitter(data=recall,aes(color=oddballtype, x=wordposition, y=normrec),    position=position_jitterdodge(dodge.width=0.9), show.legend=FALSE, alpha=0.2)+
  guides(col = FALSE)+
  scale_color_manual(values=c('orchid', 'deepskyblue'))+
  scale_fill_manual(values=c('thistle1','lightblue1'), labels=c('Emotional','Perceptual'), name='Oddball List Type')+
  scale_x_discrete(
    labels = c("Odd-2", "Odd-1", "Odd","Odd+1")
  )+
  #ggtitle('Normalized Recall')+
  labs(x='Word Position', y='Normalized Recall (- control)')+
  theme_classic()

#recall.fig


#Create QQ plot for each cell of design
recall.QQ<-ggqqplot(recall,'normrec',ggtheme=theme_bw())+
  facet_grid(oddballtype~wordposition, labeller='label_both')
#recall.QQ #looks fine

levene.recall<-levene_test(normrec~oddballtype*wordposition, data=recall)
#levene.recall #meets homogeneity of variances 

recall.aov<-anova_test(
  data=recall,dv=normrec,wid=subject,
  within=c(oddballtype,wordposition)
)
#recall.aov
get_anova_table(recall.aov)

#Post-hoc tests 
wp.data<-aggregate(x = recall$normrec, by = list(wordposition=recall$wordposition, subject=recall$subject), FUN = "mean")

WordPosition.pwc<-wp.data %>%
  pairwise_t_test(x~wordposition, paired=TRUE, p.adjust.method='fdr') #%>%
WordPosition.pwc  

wp.data %>%
  cohens_d(x~wordposition, paired=TRUE)

#Interaction oddballtype x word position
WordPositionxOdd.pwc<-recall %>%
  group_by(wordposition)%>%
  pairwise_t_test(normrec~oddballtype, paired=TRUE, p.adjust.method='fdr')# %>%
  #select(-df,-statistic) #remove details 
WordPositionxOdd.pwc

recall %>%
  group_by(wordposition) %>%
  cohens_d(normrec~oddballtype, paired=TRUE)

## Add p values to graph 
WordPosition.pwc <- WordPosition.pwc %>% add_xy_position(x = "wordposition")

WordPositionxOdd.pwc <- WordPositionxOdd.pwc %>% add_xy_position(x = "wordposition")

recall.fig+
  stat_pvalue_manual(WordPositionxOdd.pwc, label='{p.adj.signif}', inherit.aes=FALSE, hide.ns=TRUE, tip.length=0, bracket.nudge.y=-0.7)+
  stat_pvalue_manual(WordPosition.pwc, label='{p.adj.signif}', inherit.aes=FALSE, hide.ns=TRUE, tip.length =0, bracket.nudge.y=-0.1)
 


#Check whether e and p oddballs were better recalled than control words. 
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
oddVcont<-read.csv('v1final_recall_AP.csv')
oddVcont<-as.data.frame(oddVcont)

oddVcont$Subject<-as.factor(oddVcont$Subject)

names(oddVcont)[2] <- "em2"
names(oddVcont)[3] <- "em1"
names(oddVcont)[4] <- "e"
names(oddVcont)[5] <- "ep1"
names(oddVcont)[6] <- "pm2"
names(oddVcont)[7] <- "pm1"
names(oddVcont)[8] <- "p"
names(oddVcont)[9] <- "pp1"
names(oddVcont)[10] <- "ce"
names(oddVcont)[11] <- "cp"

oddVcont<-oddVcont[,c('Subject','em1','ce')]
oddVcont.long<-gather(oddVcont, position, recall, em1:ce, factor_key=TRUE)
#Run a t-test to see whether E-1 items were differently recalled than E control 

Em1.v.EC<-oddVcont.long %>%
  pairwise_t_test(recall~position, paired=TRUE)
Em1.v.EC

oddVcont.long %>%
  cohens_d(recall~position, paired=TRUE)


```

# Fig. S3 E-1, lag+1 correlation 

```{r echo=FALSE, warning=FALSE, message=FALSE}
em1_corr<-as.data.frame(subset(recall, oddballtype=='E' & wordposition=='m1'))
lag_corr<-as.data.frame(subset(TFCRP, oddballtype=='E' & transition=='from' & direction=='Forwards' & wordposition=='1'))

corrplot<-as.data.frame(cbind(em1_corr$normrec,lag_corr$CRP))

corrplt<-ggplot(corrplot, aes(x=V1, y=V2))+
  geom_point(shape=18, color='darksalmon')+
  geom_smooth(method=lm, se=FALSE, color='lightskyblue2')+
  ggtitle('Correlation of E-1 normalized recall and transitions from E Odd (lag +1)')+
  ylab('Lag +1 transitions from E Odd')+
  xlab('E-1 Normalized Recall')+
  theme_classic()

corrplt

cor.test(corrplot$V1, corrplot$V2,  method = "spearman", use = "complete.obs")
```
