---
title: "CRP_Oddball_Modulation"
author: "Peris-Yague et al. 2021"
date: "8/17/2021"
output:
  word_document: default
  pdf_document: default
  html_document:
    df_print: paged
---

```{r  echo=FALSE, results='hide', message=FALSE, warning=FALSE}
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)

#Install all libraries 

library(tidyverse)
library(ggpubr)
library(rstatix)
library(rsample)
library(dplyr)
library(ggplot2)
library(data.table)
library(effects)
library(lme4)
library(plyr)
library(emmeans)
```

<<<<<<< HEAD

# Fig. 1C Relative Recall Position by SOA 


```{r echo=FALSE, warning=FALSE, message=FALSE} 
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
RR<-read.csv('RR.csv') #Data on a trial-by-trial basis
=======
Normality was checked with QQ plots and/or histograms and homogeneity of variances was tested with levene's test. 

# Fig. 1 Relative Recall Position by SOA 

- QQ plots do not show a normal distribution 
- Homogeneity of variances is violated (p=0.00083)
- Plotted a histogram of the relative recall distribution and of the residuals of the following model:  glmer(relativerecall ~ oddballtype * SOA + (1|subject), data = RR). I think I can run a different distribution family of the model to account for the non-normal distribution. I posted a question on a stats forum https://stats.stackexchange.com/questions/540418/how-can-i-run-a-glm-on-a-left-skewed-not-normally-distributed-dv and someone suggested using a ***binomial distribution*** however I do not understand why. 
- How about the violation of homogeneity of variances, how can we deal with this?

```{r echo=FALSE, warning=FALSE, message=FALSE} 
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
RR<-read.csv('RR.csv')
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
RR<-as.data.frame(RR)
#head(RR) #to show you what my raw data looks like 
RR$oddballtype<-factor(RR$oddballtype)
RR$SOA<-factor(RR$SOA)
RR$subject<-factor(RR$subject)

RR.plot.SOA.data<- RR %>%
  group_by(SOA, oddballtype) %>%
  get_summary_stats(relativerecall, type='mean_ci')

<<<<<<< HEAD
#calculate mean for emotional and perceptual
mean.calc<- RR %>%
  group_by(oddballtype) %>%
  get_summary_stats(relativerecall,type='mean_ci')
  

RR.SOA.plt2<-ggplot(RR.plot.SOA.data, aes(x=SOA,y=mean, group=oddballtype, shape=oddballtype, color=SOA, ymin=mean-ci, ymax=mean+ci))+ 
  geom_pointrange(position=position_dodge(width=0.5), size=1)+
  scale_color_brewer(palette='Set2')+
  theme_classic()+
  theme(strip.background=element_blank(), text=element_text(size=17))+
  xlab('Stimulus Onset Asynchrony')+
  ylab('Relative Recall Position')+
  labs(color='SOA', shape='Oddball Type')+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))

#Now let's run a 2-way ANOVA with oddball x SOA as factors on relative recall 
=======
RR.SOA.plt <- ggplot (RR.plot.SOA.data,aes(x=as.factor(SOA),y=mean, group=oddballtype, color=oddballtype))+
  geom_line(size=1) +
  geom_errorbar(data=RR.plot.SOA.data, aes(x=as.factor(SOA), ymin=mean-ci, ymax=mean+ci), width=0.2,
                size=0.5, position=position_dodge(0.05))+ 
  theme_classic()+
  theme(strip.background = element_blank())+
  scale_color_manual(values=c('hotpink', 'deepskyblue1'))+

  xlab('SOA') +
  ylab('Relative Recall ')+
  labs(color='Oddball Type')

RR.SOA.plt

#Now let's run a 2-way ANOVA with oddball x SOA as factors on relative recall 

>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
#Check normality with QQ plots
RR.SOA.QQ<-ggqqplot(RR,'relativerecall',ggtheme=theme_bw())+
  facet_grid(oddballtype~SOA, labeller='label_both')
RR.SOA.QQ #doesn't look normal
hist(RR$relativerecall)
lines(density(RR$relativerecall))

#Check homogeneity of variances
leveneRR<-levene_test(relativerecall ~ oddballtype*SOA, data=RR)
#leveneRR # homogeneity of variances is violated

<<<<<<< HEAD

#The assumption of sphericity is violated in the dataset doing a trial by trial analyses. However, data is normally distributed if averaging across SOAs per subject. 

RR.avg<-read.csv('RR_average.csv')
RR.avg<-as.data.frame(RR.avg)
RR.avg$oddballtype<-factor(RR.avg$oddballtype)
RR.avg$SOA<-factor(RR.avg$SOA)
RR.avg$subject<-factor(RR.avg$subject)

RR.avg.levene<-levene_test(relativerecall ~ oddballtype*SOA, data=RR.avg) #this is ok 
RR.avg.QQ<-ggqqplot(RR.avg,'relativerecall',ggtheme=theme_bw())+
  facet_grid(oddballtype~SOA, labeller='label_both')
RR.avg.QQ #looks roughly ok 

#DF are wrong because of missing values. Re-calculated with Prism with a mixed-effects model. 
=======
#These re NOT normally distributed so run a non-parametric ANOVA. Can this be done with glmer?

RR.SOA.glmer<-glmer(relativerecall ~ oddballtype*SOA + (1|subject), data = RR)
#Check whether residuals are normally distribued
hist(residuals(RR.SOA.glmer)) #Not really 
#Anova(RR.SOA.glmer,3)

#A beta distribution would probably fit the data better. 
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a


```

<<<<<<< HEAD

# Fig. 1D Amount of items recalled per SOA

```{r echo=FALSE,warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")

listrecallSOA<-read.csv('list_recall_SOA_R.csv')
listrecallSOA<-as.data.frame(listrecallSOA)
listrecallSOA$SOA<-factor(listrecallSOA$SOA)
listrecallSOA$subject<-factor(listrecallSOA$subject)

#Get the mean and CI of the amount of items recalled per SOA
listrecallSOAplot<-listrecallSOA %>%
  group_by(SOA) %>%
  get_summary_stats(total_recall_list,type='mean_ci')

# Plot 
list.recall.SOA.fig2<-ggplot(data=listrecallSOAplot, aes(x=as.factor(SOA), y=mean, color=SOA, min=mean-ci, ymax=mean+ci))+
  geom_pointrange(position=position_dodge(width=0.5), shape=15, size=1)+
  scale_color_brewer(palette="Set2")+
  scale_y_continuous(n.breaks=10)+
  theme_classic()+
  labs(x='Stimulus Onset Asynchrony', y='Average amount of items recalled')+
  theme(text=element_text(size=17))+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))

#Average so that we have 1 mean value of amount of items recalled per subject per SOA for statistics 
listrecallSOA.data<- listrecallSOA %>%
  group_by(SOA,subject) %>%
  get_summary_stats(total_recall_list, type='mean')

listrecallSOA.data<-listrecallSOA.data[-c(3,4)]
names(listrecallSOA.data)[3] <- "total_recall_list"

listrecallSOA.data<-as.data.frame(listrecallSOA.data)
listrecallSOA.data$SOA<-as.factor(listrecallSOA.data$SOA)
listrecallSOA.data$subject<-as.factor(listrecallSOA.data$subject)
listrecallSOA.data$total_recall_list<-as.numeric(listrecallSOA.data$total_recall_list)

#Check normal distribution 
list.recall.SOA.QQ<-ggqqplot(listrecallSOA.data,'total_recall_list',ggtheme=theme_bw())+
  facet_grid(~SOA, labeller='label_both') 

list.recall.SOA.QQ# looks fine 

# Run an ANOVA
listrecallSOA.aov<-anova_test(
  data=listrecallSOA.data,dv=total_recall_list,wid=subject, 
  within=c(SOA),
)

get_anova_table(listrecallSOA.aov)

#Re-structure the data in case we want to run this with Prism or JASP
  
listrecallSOA.wide<-reshape(listrecallSOA, idvar = 'subject', timevar = 'SOA', direction = 'wide')
names(listrecallSOA.wide)[2] <- "SOA 6"
names(listrecallSOA.wide)[3] <- "SOA 3"
names(listrecallSOA.wide)[4] <- "SOA 2"
names(listrecallSOA.wide)[5] <- "SOA 1"
names(listrecallSOA.wide)[6] <- "SOA 4"


path_out<-'/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results/'
write.csv(listrecallSOA.data.aov,paste(path_out,'Fig1D_prism.csv',sep = ''))

```


# Fig. 2A Conditional Response Probability Curves

=======
# In-text analysis- Normalized Recall by SOA 
- QQ plots show normal distribution 
- Levene's test p>0.05
- Ran a RM ANOVA with factors oddballtype x lag x SOA 
```{r echo=FALSE, warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
recallSOA<-read.csv('normrec_SOA_R.csv')
recallSOA<-as.data.frame(recallSOA)
#head(recallSOA) #to show you what my raw data looks like 
recallSOA$subject<-factor(recallSOA$subject)
recallSOA$oddballtype<-factor(recallSOA$oddballtype)
recallSOA$wordposition<-factor(recallSOA$wordposition)
recallSOA$SOA<-factor(recallSOA$SOA)

recSOAplot<-recallSOA %>%
  group_by(oddballtype,wordposition, SOA) %>%
  get_summary_stats(normrec,type='mean_ci')#%>%
  #View()

recSOAplot<-rename(recSOAplot, c('normrec'=mean))
  
recall.SOA.fig<-ggplot(recSOAplot, aes(fill=oddballtype, x=wordposition, y=normrec))+
  geom_bar(position='dodge', stat='identity')+
  geom_errorbar(aes(x=wordposition, ymin=normrec-ci, ymax=normrec+ci), width=0.4, color='wheat4',
                size=0.5, position=position_dodge(0.9), stat='identity')+
  geom_jitter(data=recallSOA,aes(color=oddballtype, x=wordposition, y=normrec), position=position_jitterdodge(dodge.width=0.9), show.legend=FALSE, alpha=0.07)+
  guides(col = FALSE)+
  scale_color_manual(values=c('orchid', 'deepskyblue'))+
  scale_fill_manual(values=c('thistle1','lightblue1'), labels=c('Emotional','Perceptual'), name='Oddball Type')+
  scale_x_discrete(
    labels = c("Odd-2", "Odd-1", "Odd","Odd+1")
  )+
  ggtitle('Normalized Recall by SOA')+
  labs(x='Word Position', y='Normalized Recall (- control)')+
  facet_wrap(~ SOA, ncol=3)+
  theme_classic()
#recall.SOA.fig

#Create QQ plot to test for normality 
recall.SOA.QQ<-ggqqplot(recallSOA,'normrec',ggtheme=theme_bw())+
  facet_grid(oddballtype+wordposition~SOA, labeller='label_both') # looks fine 

recall.SOA.QQ

levene.recall.SOA<-levene_test(normrec~oddballtype*wordposition*SOA, data=recallSOA)
#levene.recall.SOA #meets homogeneity of variances 

recallSOA.aov<-anova_test(
  data=recallSOA,dv=normrec,wid=subject,
  within=c(oddballtype,wordposition,SOA)
)

#recallSOA.aov
get_anova_table(recallSOA.aov)

#Post-hoc tests
#Main effect of word position 
WordPositionSOA.pwc<-recallSOA %>%
  pairwise_t_test(normrec~wordposition, paired=TRUE, p.adjust.method='fdr') #%>%
WordPositionSOA.pwc  

recallSOA %>%
  cohens_d(normrec~wordposition, paired=TRUE)

#Main effect of SOA
SOA.pwc<-recallSOA %>%
  pairwise_t_test(normrec~SOA, paired=TRUE, p.adjust.method='fdr') #%>%
SOA.pwc

recallSOA %>%
  cohens_d(normrec~SOA, paired=TRUE)

#Interaction oddballtype x word position

WordPositionxOddSOA.pwc<-recallSOA %>%
  group_by(wordposition)%>%
  pairwise_t_test(normrec~oddballtype, paired=TRUE, p.adjust.method='fdr') #%>%
WordPositionxOddSOA.pwc

recallSOA %>%
  group_by(wordposition) %>%
  cohens_d(normrec~oddballtype, paired=TRUE) 
```

# Fig. 2A Conditional Response Probability Curves

- QQ plots look normal 
- Levene's test shows p<0.0001 --> homogeneity of variances is violated. How can we deal with this?

At the moment, data was analyzed with a RM ANOVA with factors oddballtype x lag x direction 
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a

```{r echo=FALSE,warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
CRPall<-read.csv('CRP_all_R.csv')
CRPall<-as.data.frame(CRPall)

<<<<<<< HEAD
#Get the mean per subject per word position and direction 
=======
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
crpplot<-CRPall %>%
  group_by(oddballtype,wordposition, direction) %>%
  get_summary_stats(CRP,type='mean_se')

## This is needed to make the 'backwards' lags negative so that they plot
# correctly 
wpplot<-numeric(0)
for (rows in 1:nrow(crpplot)){
  if (crpplot$direction[rows] == "Backwards") {
    wpplot[rows]<-(crpplot$wordposition[rows])*-1
  }
  else {wpplot[rows]<-(crpplot$wordposition[rows])
  }
}
invisible(as.data.frame(wpplot))
crpplot$wpplot<-wpplot

pltCRP<-ggplot(crpplot,aes(x=wpplot,y=mean), group=oddballtype)+
<<<<<<< HEAD
        geom_line(aes(color=oddballtype), size=1) +
        geom_point(aes(color=oddballtype), size=2) +
        theme_classic()+
        facet_wrap(~ direction, scales='free_x', ncol=2)+    
        theme(strip.background = element_blank())+
        theme(text=element_text(size=17))+
=======
        geom_line(aes(color=oddballtype)) +
        geom_point(aes(color=oddballtype)) +
        theme_classic()+
        facet_wrap(~ direction, scales='free_x')+    
        theme(strip.background = element_blank())+
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
        #ggtitle('CRP all')+
        xlab('Lag') +
        ylab('Conditional Response Probability')+
        scale_color_manual(values=c('violetred2','turquoise2'), 
<<<<<<< HEAD
          labels=c('Emotional','Perceptual'), name='Oddball List Type')+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))
=======
          labels=c('Emotional','Perceptual'), name='Oddball List Type')
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
                    
pltCRP

CRPall$subject<-factor(CRPall$subject)
CRPall$oddballtype<-factor(CRPall$oddballtype)
CRPall$direction<-factor(CRPall$direction)
CRPall$wordposition<-factor(CRPall$wordposition)

#Check for normality and homogeneity of variances 

CRP.QQ<-ggqqplot(CRPall,'CRP',ggtheme=theme_bw())+
  facet_grid(oddballtype+direction~wordposition, labeller='label_both') 

CRP.QQ # looks fine 

<<<<<<< HEAD
#If homogeneity of variances is violated, sphericity is automatically corrected in get_anova_table with Greenhouse-Geisser correction. 
=======
leveneCRPall<-levene_test(CRP ~ oddballtype*wordposition*direction, data=CRPall)
#leveneCRPall #homogeneity of variances is violated 
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a

#Run RM ANOVA
CRPall.aov<-anova_test(
  data=CRPall,dv=CRP,wid=subject,
  within=c(oddballtype,wordposition,direction)
)
CRPall.aov
get_anova_table(CRPall.aov)

<<<<<<< HEAD
#Interaction word position x direction 

WpxDir.data<-aggregate(x = CRPall$CRP, by = list(wordposition=CRPall$wordposition, direction=CRPall$direction, subject=CRPall$subject), FUN = "mean")

WpxDir.pwc1<- WpxDir.data %>%
  group_by(direction) %>%
  pairwise_t_test(x~wordposition,paired=TRUE, p.adjust.method='fdr')

WpxDir.data %>%
  group_by(direction) %>%
  cohens_d(x~wordposition, paired=TRUE)

WpxDir.pwc2<- WpxDir.data %>%
  group_by(wordposition) %>%
  pairwise_t_test(x~direction,paired=TRUE, p.adjust.method='fdr')

WpxDir.data %>%
  group_by(wordposition) %>%
  cohens_d(x~direction, paired=TRUE)




=======
#Follow-up t-tests 
#Main effect of oddballtype
CRPoddballtype.pwc<-CRPall %>%
  pairwise_t_test(CRP~oddballtype, paired=TRUE, p.adjust.method='fdr') 
CRPoddballtype.pwc

CRPall %>%
  cohens_d(CRP~oddballtype, paired=TRUE)

#Main effect of word position
CRPwordposition.pwc<-CRPall %>%
  pairwise_t_test(CRP~wordposition, paired=TRUE, p.adjust.method='fdr') 
CRPwordposition.pwc

CRPall %>%
  cohens_d(CRP~wordposition, paired=TRUE)

#Interaction direction x word position

DirectionxWordPosition.pwc<-CRPall %>%
  group_by(wordposition)%>%
  pairwise_t_test(CRP~direction, paired=TRUE, p.adjust.method='fdr') 
DirectionxWordPosition.pwc

CRPall %>%
  group_by(wordposition) %>%
  cohens_d(CRP~direction, paired=TRUE)
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
```



# Fig. 2B Conditional Response Probability Curves by Stimulus Onset Asynchrony

<<<<<<< HEAD
```{r echo=FALSE, warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
CRPSOA<-read.csv('all_CRP_SOA_R.csv')
=======
- QQ plots do not show a normal distribution, plotted a histogram of the data and a histogram of the residuals of the following model glmer(CRP ~ wordposition * direction * SOA + (1|subject), data = CRPSOA). 
- Levene's test p<0.0001 --> homogeneity of variances not met 

- How should we proceed to analyze this? Maybe with a different family of distributions in the glmer?

```{r echo=FALSE, warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
CRPSOA<-read.csv('ToFrom_CRP_SOA_R.csv')
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
CRPSOA<-as.data.frame(CRPSOA)

CRPSOAplot<-CRPSOA %>%
  group_by(wordposition, direction, SOA) %>%
  get_summary_stats(CRP,type='mean_se')

wpplot<-numeric(0)
for (rows in 1:nrow(CRPSOAplot)){
  if (CRPSOAplot$direction[rows] == "Backwards") {
    wpplot[rows]<-(CRPSOAplot$wordposition[rows])*-1
  }
  else {wpplot[rows]<-(CRPSOAplot$wordposition[rows])
  }
}
invisible(as.data.frame(wpplot))
CRPSOAplot$wpplot<-wpplot

#factor all the categorical variables 
CRPSOA$SOA<-factor(CRPSOA$SOA)
CRPSOA$direction<-factor(CRPSOA$direction)
CRPSOA$wordposition<-factor(CRPSOA$wordposition)
CRPSOA$subject<-factor(CRPSOA$subject)
CRPSOA$oddballtype<-factor(CRPSOA$oddballtype)
<<<<<<< HEAD

pltCRPSOA<-ggplot(CRPSOAplot,aes(x=wpplot,y=mean, group=SOA, color=as.factor(SOA)))+
  geom_line(size=1) +
  geom_point(size=2) +
  theme_classic()+
  facet_wrap(~ direction, scales='free_x', ncol=2)+ 
  theme(strip.background = element_blank())+
  theme(text=element_text(size=17))+
  xlab('Lag') +
  ylab('Conditional Response Probability')+
  scale_color_brewer(palette="Set2")+
  labs(color='SOA')+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))

pltCRPSOA

#Get the means averaging across oddball types and lags to have a value per subject per SOA in the forwards and backwards direction.   
CRP.SOA.data<-aggregate(x = CRPSOA$CRP, by = list(SOA=CRPSOA$SOA, direction=CRPSOA$direction, subject=CRPSOA$subject), FUN = "mean")

#subset data only in the forwards direction to investigate whether the forwardness differs accross SOAs (averaging on both oddball types and across 5 lags)
CRP.SOA.data<-as.data.frame(subset(CRP.SOA.data, direction=='Forwards'))

CRP.SOA.QQ<-ggqqplot(CRP.SOA.data,'x',ggtheme=theme_bw())+
  facet_grid(~SOA, labeller='label_both') 

#Run a one-way ANOVA
CRPall.SOA.aov<-anova_test(
  data=CRP.SOA.data,dv=x,wid=subject,
  within=c(SOA)
)
CRPall.SOA.aov
get_anova_table(CRPall.SOA.aov)

#Run follow-up t-tests 
SOA.pwc<- CRP.SOA.data %>%
  pairwise_t_test(x~SOA,paired=TRUE, p.adjust.method='fdr')

CRP.SOA.data %>%
  cohens_d(x~SOA, paired=TRUE)

  
```


# Fig. 3C Conditional Response Probability Curves transitions ***to*** and ***from*** oddballs

=======
CRPSOA$transition<-factor(CRPSOA$transition)

pltCRPSOA<-ggplot(CRPSOAplot,aes(x=wpplot,y=mean, group=SOA, color=as.factor(SOA)))+
  geom_line() +
  geom_point() +
  theme_classic()+
  facet_wrap(~ direction, scales='free_x', ncol=2)+ 
  theme(strip.background = element_blank())+
  xlab('Lag') +
  ylab('Conditional Response Probability')+
  scale_color_brewer(palette="Set2")+
  labs(color='SOA')

pltCRPSOA

#Assess Normality 

CRP.SOA.QQ<-ggqqplot(CRPSOA,'CRP',ggtheme=theme_bw())+
  facet_grid(oddballtype+direction~SOA, labeller='label_both') 

CRP.SOA.QQ #Does not look normally distributed 
hist(CRPSOA$CRP) #Distribution of our current data 

levene.CRP.SOA<-levene_test(CRP~wordposition*direction*SOA, data=CRPSOA)
#levene.CRP.SOA #homogeneity of variances NOT met 

CRPSOA_glmer<-glmer(CRP ~ wordposition*direction*SOA + (1|subject), data = CRPSOA)
hist(residuals(CRPSOA_glmer)) #Residuals not normally distributed 
Anova(CRPSOA_glmer,3)

#Main effect of word position 
#plot(effect('wordposition',CRPSOA_glmer))

    CRPSOA %>%
  pairwise_t_test(CRP~wordposition, paired=TRUE, p.adjust.method='fdr')
    
    CRPSOA %>%
  cohens_d(CRP~wordposition, paired=TRUE)

#Main effect of SOA
#plot(effect('SOA',CRPSOA_glmer))

CRPSOA %>%
  pairwise_t_test(CRP~SOA, paired=TRUE, p.adjust.method='fdr')

CRPSOA %>%
  cohens_d(CRP~SOA, paired=TRUE)
```


# Fig. 2C Amount of items recalled per SOA
- QQ plots and histograms look roughly OK 
- Levene's test p>0.05 
- Data analyzed with a glmer(total_recall_list~SOA+(1|subject), data=listrecallSOA) because I included each list per SOA per subject. I think if we wanted to run this as an ANOVA I would have to average them to get 1 averaged recall number per subject per SOA. What do you think is best?

```{r echo=FALSE,warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")

listrecallSOA<-read.csv('list_recall_SOA_R.csv')
listrecallSOA<-as.data.frame(listrecallSOA)
listrecallSOA$SOA<-factor(listrecallSOA$SOA)
listrecallSOA$subject<-factor(listrecallSOA$subject)

listrecallSOAplot<-listrecallSOA %>%
  group_by(SOA) %>%
  get_summary_stats(total_recall_list,type='mean_ci')

list.recall.SOA.fig<-ggplot(data = listrecallSOAplot,mapping = aes(x = as.factor(SOA), y = mean, fill=SOA))+
  geom_bar(position='dodge', stat='identity')+
  geom_errorbar(aes(x=as.factor(SOA), ymin=mean-ci, ymax=mean+ci), width=0.4, color='black',
                size=0.8, position=position_dodge(0.8), stat='identity')+
    labs(x='Stimulus Onset Asynchronies (SOA)', y='Items recalled ')+     
    scale_y_continuous(n.breaks=14)+
    scale_fill_brewer(palette='Set2')+
    theme_classic()

list.recall.SOA.fig + geom_jitter(data=listrecallSOA,mapping =aes(x=SOA, y=total_recall_list), alpha=0.1)

#Check normal distribution 
list.recall.SOA.QQ<-ggqqplot(listrecallSOA,'total_recall_list',ggtheme=theme_bw())+
  facet_grid(~SOA, labeller='label_both') 

list.recall.SOA.QQ# looks fine 

levene.recall.SOA<-levene_test(total_recall_list ~ SOA, data=listrecallSOA)
#levene.recall.SOA #looks fine 

hist(listrecallSOA$total_recall_list)

list.recall.SOA.glmer<- glmer(total_recall_list~SOA+(1|subject), data=listrecallSOA) 
hist(residuals(list.recall.SOA.glmer)) #Residuals look normally distributed 

Anova(list.recall.SOA.glmer,3)
```

# Fig. 3C Conditional Response Probability Curves transitions ***to*** and ***from*** oddballs
- We collapsed accross lags and used 'omitnan' in Matlab for statistical analyses
- QQ plots show a normal distribution 
- Levene's test p=0.00011--> homogeneity of variances NOT met. Can we still analyze the data with the RM ANOVA?

The collapsed data was analyzed with a RM ANOVA with factors oddballtype, direction and transition. 

- For the figure and plotting we used all data points between lags 1-5
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
```{r echo=FALSE, warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
TFCRP<-read.csv('ToFrom_CRP_R.csv')
TFCRP<-as.data.frame(TFCRP)
#head(TFCRP) #to show you what my raw data looks like 

TFplot<-TFCRP %>%
  group_by(oddballtype,wordposition, direction,transition) %>%
  get_summary_stats(CRP,type='mean_se')

wpplot<-numeric(0)
for (rows in 1:nrow(TFplot)){
  if (TFplot$direction[rows] == "Backwards") {
    wpplot[rows]<-(TFplot$wordposition[rows])*-1
  }
  else {wpplot[rows]<-(TFplot$wordposition[rows])
  }
}
invisible(as.data.frame(wpplot))
TFplot$wpplot<-wpplot
TFplot$transition<-factor(TFplot$transition, levels=c('to','from'))

transition.labs<- c('Transition TO the oddball', 'Transition FROM the oddball')
names(transition.labs)<-c('to', 'from')


pltTF<-ggplot(TFplot,aes(x=wpplot,y=mean), group=oddballtype)+
<<<<<<< HEAD
  geom_line(aes(color=oddballtype), size=1) +
  geom_point(aes(color=oddballtype), size=2) +
=======
  geom_line(aes(color=oddballtype)) +
  geom_point(aes(color=oddballtype)) +
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
   theme_classic()+
  facet_grid(transition~direction, scales='free_x', 
             labeller=labeller(transition = as_labeller(transition.labs)))+   
  theme(strip.background = element_blank())+
<<<<<<< HEAD
  theme(text=element_text(size=17))+
=======
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
  #ggtitle('CRP transitions to and from the oddballs')+
  xlab('Lag') +
  ylab('Conditional Response Probability')+
  scale_color_manual(values=c('violetred2','turquoise2'), 
<<<<<<< HEAD
                     labels=c('Emotional','Perceptual'), name='Oddball List Type')+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))
=======
                     labels=c('Emotional','Perceptual'), name='Oddball List Type')
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
 

pltTF

TFCRP$subject<-factor(TFCRP$subject)
TFCRP$oddballtype<-factor(TFCRP$oddballtype)
TFCRP$transition<-factor(TFCRP$transition)
TFCRP$direction<-factor(TFCRP$direction)
TFCRP$wordposition<-factor(TFCRP$wordposition)

#Collapsing accross lags 'omitnan'
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
TFCRP_collapsed<-read.csv('collapsed_CRP_omitnan.csv')
TFCRP_collapsed<-as.data.frame(TFCRP_collapsed)

TF.QQ<-ggqqplot(TFCRP_collapsed,'CRPmean',ggtheme=theme_bw())+
  facet_grid(oddballtype+direction~transition, labeller='label_both') 
TF.QQ # QQ plots look fine 

levene.TF<-levene_test(CRPmean ~ oddballtype*direction*transition, data=TFCRP_collapsed)
<<<<<<< HEAD
#levene.TF #assumption violated, however, this doesn't apply to our data because we have only 2 levels for each IV (factor)
=======
#levene.TF #assumption violated 
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a

TFCRP_collapsed$subject<-as.factor(TFCRP_collapsed$subject)
TFCRP_collapsed$oddballtype<-as.factor(TFCRP_collapsed$oddballtype)
TFCRP_collapsed$transition<-as.factor(TFCRP_collapsed$transition)
TFCRP_collapsed$direction<-as.factor(TFCRP_collapsed$direction)


TF.collapsed.aov<-anova_test(
  data=TFCRP_collapsed,dv=CRPmean,wid=subject, 
  within=c(oddballtype,direction,transition),
)
<<<<<<< HEAD
get_anova_table(TF.collapsed.aov)

#Oddballtype x transition interaction 
OddxTr.data<-aggregate(x = TFCRP_collapsed$CRPmean, by = list(transition=TFCRP_collapsed$transition, oddballtype=TFCRP_collapsed$oddballtype, subject=TFCRP_collapsed$subject), FUN = "mean")

OddxTr.pwc<- OddxTr.data %>%
  group_by(oddballtype) %>%
  pairwise_t_test(x~transition, paired=TRUE, p.adjust.method = 'fdr')


OddxTr.data %>%
  group_by(oddballtype) %>%
  cohens_d(x~transition, paired=TRUE)

#Direction x transition interaction 
DirxTr.data<-aggregate(x = TFCRP_collapsed$CRPmean, by = list(transition=TFCRP_collapsed$transition, direction=TFCRP_collapsed$direction, subject=TFCRP_collapsed$subject), FUN = "mean")

DirxTr.pwc<- DirxTr.data %>%
  group_by(direction) %>%
  pairwise_t_test(x~transition, paired=TRUE, p.adjust.method = 'fdr')


DirxTr.data %>%
  group_by(direction) %>%
  cohens_d(x~transition, paired=TRUE)


#Plot 2 for inspecting the results 
=======
TF.collapsed.aov #this isn't showing Mauchly's test results because sphericity is only calculated when the IV have 3 or + levels. 
get_anova_table(TF.collapsed.aov)

odd.collapsed.pwc<-TFCRP_collapsed %>%
  pairwise_t_test(CRPmean~oddballtype, paired=TRUE, p.adjust.method='fdr') #%>%
odd.collapsed.pwc

TFCRP_collapsed %>%
  cohens_d(CRPmean~oddballtype, paired=TRUE)

#ggboxplot(TFCRP_collapsed, x = "oddballtype", y = "CRPmean") 

transition.collapsed.pwc<-TFCRP_collapsed %>%
  pairwise_t_test(CRPmean~transition, paired=TRUE, p.adjust.method='fdr') #%>%
transition.collapsed.pwc

TFCRP_collapsed %>%
  cohens_d(CRPmean~transition, paired=TRUE)

#ggboxplot(TFCRP_collapsed, x = "transition", y = "CRPmean") 

OddxTr.collapsed.pwc<-TFCRP_collapsed %>%
  group_by(oddballtype)%>%
  pairwise_t_test(CRPmean~transition, paired=TRUE, p.adjust.method='fdr') #%>%
OddxTr.collapsed.pwc

TFCRP_collapsed %>%
  group_by(oddballtype) %>%
  cohens_d(CRPmean~transition, paired=TRUE)

#ggboxplot(TFCRP_collapsed, x = "transition", y = "CRPmean", color='oddballtype') 

DirxTr.collapsed.pwc<-TFCRP_collapsed %>%
  group_by(direction)%>%
  pairwise_t_test(CRPmean~transition, paired=TRUE, p.adjust.method='fdr') #%>%
DirxTr.collapsed.pwc

TFCRP_collapsed %>%
  group_by(direction) %>%
  cohens_d(CRPmean~transition, paired=TRUE)

#ggboxplot(TFCRP_collapsed, x = "transition", y = "CRPmean", color='direction') 

>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
transition.labs<- c('Transition TO the oddball', 'Transition FROM the oddball')
names(transition.labs)<-c('to', 'from')

neworder <- c("to","from")
TFCRP_collapsed.neworder <- arrange(transform(TFCRP_collapsed,
             transition=factor(transition,levels=neworder)),transition)

pltTF.collapsed<-ggplot(TFCRP_collapsed,aes(x=direction,y=CRPmean), group=oddballtype)+
  geom_boxplot(aes(color=oddballtype)) +
   theme_classic()+
  facet_grid(~transition, scales='free_x', 
             labeller=labeller(transition = as_labeller(transition.labs)))+   
<<<<<<< HEAD
  theme(text=element_text(size=17))+
=======
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
  theme(strip.background = element_blank())+
  xlab('Collapsed Lag') +
  ylab('Conditional Response Probability')+
  scale_color_manual(values=c('violetred2','turquoise2'), 
                     labels=c('Emotional','Perceptual'), name='Oddball Type')

#pltTF.collapsed

```
# Fig. 4 Condutional Response Probability Curves by SOA transitions ***to*** and ***from*** oddballs

<<<<<<< HEAD
=======
Only focusing on emotional oddballs, collapsing accross lags 'omitnan'

- QQ plots do not show a normal distribution 
- Levene's test p<0.0001--> homogeneity of variances violated. 

Data was analyzed with a glmer then, glmer(CRPmean ~ direction * transition * SOA + (1|subject), data = data_collapsed). 
- The histogram of the residual plot of the model looks 'roughly' normal--> is this analysis OK then? What can we do about the violation of homogeneity of variances?
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a

```{r echo=FALSE, warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
data_collapsed<-read.csv('E_lag_collapsed_R.csv')
data_collapsed<-as.data.frame(data_collapsed)

data_collapsed$subject<-factor(data_collapsed$subject)
data_collapsed$SOA<-factor(data_collapsed$SOA)
data_collapsed$transition<-factor(data_collapsed$transition)
data_collapsed$direction<-factor(data_collapsed$direction)

### Plot data ###
plot3w <-data_collapsed %>%
  group_by(direction, transition,SOA) %>%
  get_summary_stats(CRPmean,type='mean_ci')#%>%

<<<<<<< HEAD
#Reorganize the df to plot in the correct order
=======
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
neworder <- c("to","from")
plot3w.order <- arrange(transform(plot3w,
             transition=factor(transition,levels=neworder)),transition)

<<<<<<< HEAD
CRPSOA.plt<-ggplot(plot3w.order, aes(x=SOA,y=mean, group=direction, shape=direction, color=SOA,  ymin=mean-ci, ymax=mean+ci))+ 
geom_pointrange(position=position_dodge(width=0.5), size=1)+
  scale_shape_manual(values=c(1, 16))+
=======

#these are CI 
CRPSOA.plt<-ggplot(plot3w.order, aes(x=SOA,y=mean, group=direction, color=SOA, shape=direction, ymin=mean-ci, ymax=mean+ci))+ 
  geom_pointrange(position=position_dodge(width=0.5))+
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
  facet_grid(~transition)+
  scale_color_brewer(palette="Set2")+
  labs(color='SOA')+
  ylab('Conditional Response Probability')+
<<<<<<< HEAD
  xlab('Stimulus Onset Asynchrony')+
  theme_classic()+
  theme(text=element_text(size=17))+
  theme(strip.background = element_blank())+
  scale_y_continuous(
  labels = scales::number_format(accuracy = 0.01))
=======
  theme_classic()+
  theme(strip.background = element_blank())
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a

CRPSOA.plt


#Check Normality 
TF.SOA.QQ<-ggqqplot(data_collapsed,'CRPmean',ggtheme=theme_bw())+
  facet_grid(direction+transition~SOA, labeller='label_both') 
<<<<<<< HEAD
TF.SOA.QQ #not normally distributed 
hist(data_collapsed$CRPmean)
=======
TF.SOA.QQ #Some look a bit off 
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a

levene.TF.SOA<-levene_test(CRPmean ~ direction*transition*SOA, data=data_collapsed)
#levene.TF.SOA #assumption violated 

<<<<<<< HEAD
#Run separate non parametric tests
TovFrom.CRP.SOA <- data_collapsed %>%
  group_by(transition, subject) %>%
  get_summary_stats(CRPmean,type='mean_ci')


TovFrom.wilcox<- TovFrom.CRP.SOA %>%
  wilcox_test(mean~transition, paired=TRUE) 

TovFrom.wilcox.effsize<- TovFrom.CRP.SOA %>%
  wilcox_effsize(mean~transition, paired=TRUE) 

#check which mean is larger 
data_collapsed %>%
  group_by(transition) %>%
  get_summary_stats(CRPmean,type='mean_ci')

path_out<-'/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results/'
write.csv(TovFrom.CRP.SOA,paste(path_out,'Fig4_intext_prism.csv',sep = ''))


#stats to assess whether transitions from emotional oddballs at SOA 1 were different than the others. 

BvF.from.SOA<- data_collapsed %>%
  group_by(direction, SOA, subject, transition) %>%
  get_summary_stats(CRPmean, type='mean_ci')

BvF.from.SOA<-as.data.frame(subset(BvF.from.SOA, transition=='from'))


#subset data in the forwards direction 
F.from.SOA<-as.data.frame(subset(BvF.from.SOA, direction=='forwards'))

F.from.SOA.wide<-reshape(F.from.SOA, idvar = "subject", timevar = "SOA", direction = "wide")
F.from.SOA.wide<-F.from.SOA.wide[,c('subject','mean.1','mean.2','mean.3','mean.4','mean.6')] #contains subject, SOA is each column and CRP mean inside


#rename the columns 
names(F.from.SOA.wide)[2] <- "1"
names(F.from.SOA.wide)[3] <- "2"
names(F.from.SOA.wide)[4] <- "3"
names(F.from.SOA.wide)[5] <- "4"
names(F.from.SOA.wide)[6] <- "6"

#save data to run the Friedman test on Prism 
path_out<-'/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results/'
write.csv(F.from.SOA.wide,paste(path_out,'Fig4_Forward_from_SOA_jasp.csv',sep = ''))


=======
collapsed_glm <- glmer(CRPmean ~ direction*transition*SOA + (1|subject), data = data_collapsed)
hist(residuals(collapsed_glm)) #Do these look 'normal'?
Anova(collapsed_glm,3)

#plot(effect('direction*transition*SOA',collapsed_glm))
#plot(effect('direction*transition', collapsed_glm))

hist(data_collapsed$CRPmean)

meanDirxTrxSOA<-emmeans(collapsed_glm,~ direction*transition*SOA, adjust='fdr' )
posthoc1<-pairs(meanDirxTrxSOA, adjust='fdr')
eff_size(meanDirxTrxSOA, sigma=sigma(collapsed_glm), edf=df.residual(collapsed_glm))

meanDirxTr<-emmeans(collapsed_glm,~ direction*transition, adjust='fdr')
posthoc2<-pairs(meanDirxTr, adjust='fdr')
eff_size(meanDirxTr, sigma=sigma(collapsed_glm), edf=df.residual(collapsed_glm))

#calculate how many NaNs
data_collapsed %>%
  group_by(SOA) %>%
  summarise_each(funs(sum(is.na(.))))
 
#total observations
data_collapsed  %>%
  group_by(SOA) %>%
  dplyr::summarise(n=n())
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a

```





# ***Supplementary Material Analyses***

# Fig. S1 Conditional Response Probability Curves in remembered vs. forgotten oddballs 
<<<<<<< HEAD

=======
- QQ plots look OK 
- Levene's test p<0.0001--> homogeneity of variances violated 
- Data analyzed with a RM ANOVA with factors: oddballtype x direction x lag x recall. This is a 4-way anova and I do not think it's that informative. I think we should remove it from the paper. 
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
```{r echo=FALSE,warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
RvF<-read.csv('rvf_CRP_R.csv')
RvF<-as.data.frame(RvF)
#head(RvF) #to show you what my raw data looks like 

rvfplot<-RvF %>%
  group_by(oddballtype,wordposition, direction,recall) %>%
  get_summary_stats(CRP,type='mean_se')

wpplot<-numeric(0)
for (rows in 1:nrow(rvfplot)){
  if (rvfplot$direction[rows] == "Backwards") {
    wpplot[rows]<-(rvfplot$wordposition[rows])*-1
  }
  else {wpplot[rows]<-(rvfplot$wordposition[rows])
  }
}
invisible(as.data.frame(wpplot))
rvfplot$wpplot<-wpplot

pltRVF<-ggplot(rvfplot,aes(x=wpplot,y=mean), group=oddballtype)+
  geom_line(aes(color=oddballtype)) +
  geom_point(aes(color=oddballtype)) +
  facet_wrap(~ recall + direction, scales='free_x')+   
  #ggtitle('CRP forgotten vs. recalled oddballs')+
  xlab('Lag') +
  ylab('Conditional Response Probability')+
  scale_color_manual(values=c('violetred2','turquoise2'), 
                     labels=c('Emotional','Perceptual'), name='Oddball List Type')+
  theme_classic()
pltRVF

<<<<<<< HEAD
=======
RvF$subject<-factor(RvF$subject)
RvF$oddballtype<-factor(RvF$oddballtype)
RvF$recall<-factor(RvF$recall)
RvF$direction<-factor(RvF$direction)
RvF$wordposition<-factor(RvF$wordposition)

RVF.QQ<-ggqqplot(RvF,'CRP',ggtheme=theme_bw())+
  facet_grid(oddballtype+direction+recall~wordposition, labeller='label_both') # looks fine 

RVF.QQ
levene.RVF<- levene_test(CRP~oddballtype*wordposition*direction*recall, data=RvF)
#levene.RVF #Does NOT meet homogeneity of variances


RvF.aov<-anova_test(
  data=RvF,dv=CRP,wid=subject,
  within=c(oddballtype,wordposition,direction,recall)
)
RvF.aov
get_anova_table(RvF.aov)

#Main effect of word position
RvFwordposition.pwc<-RvF %>%
  pairwise_t_test(CRP~wordposition, paired=TRUE, p.adjust.method='fdr') #%>%
#select(-df,-statistic) #remove details 
RvFwordposition.pwc

RvF %>%
  cohens_d(CRP~wordposition, paired=TRUE)

#Main effect of recall 
RvFrecall.pwc<-RvF %>%
  pairwise_t_test(CRP~recall, paired=TRUE, p.adjust.method='fdr') #%>%
  #select(-df,-statistic) #remove details 
RvFrecall.pwc

RvF %>%
  cohens_d(CRP~recall, paired=TRUE)

#Interaction direction x word position

DirectionxWordPosition.RvF.pwc<-RvF %>%
  group_by(wordposition)%>%
  pairwise_t_test(CRP~direction, paired=TRUE, p.adjust.method='fdr')#%>%
  #select(-df,-statistic) #remove details 
DirectionxWordPosition.RvF.pwc

RvF %>%
  group_by(wordposition)%>%
  cohens_d(CRP~direction, paired=TRUE)
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a

```


<<<<<<< HEAD
# Fig. S2 Normalized Recall 
=======
# Fig. S2 Relative Recall Position of the Oddballs
- Normality not met--> used non-parametric t-test (Wilcoxon test)

```{r echo=FALSE,warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
RR<-read.csv('RR.csv')
RR<-as.data.frame(RR)

RR$oddballtype<-factor(RR$oddballtype)
RR$SOA<-factor(RR$SOA)
RR$subject<-factor(RR$subject)

RRplot<-RR %>%
  group_by(oddballtype) %>%
  get_summary_stats(relativerecall,type='mean_ci') #%>%
  #View()
RRplot <- dplyr::rename(RRplot, c('relativerecall' = mean))

RRnormality<-RR %>%
  group_by(oddballtype) %>%
  shapiro_test(relativerecall)#%>%
  #View()

RR.plt<-ggplot(RR,aes(x=oddballtype, y=relativerecall, fill=oddballtype))+
  geom_violin()+#(position='dodge', stat='identity')+
  geom_jitter(color='grey', size=0.4, alpha=0.9)+ 
  geom_errorbar(data=RRplot, aes(x=oddballtype, ymin=relativerecall-ci, ymax=relativerecall+ci), width=0.4, color='wheat4',
                size=0.5, position=position_dodge(0.9), stat='identity')+
  scale_fill_manual(values=c('thistle1','lightblue1'), labels=c('Emotional','Perceptual'), name='Oddball Type')+
  ggtitle('Relative Recall Position')+
  labs(x='Oddball Type', y='Relative Recall Position')+
  theme_classic()
  
RR.plt

#Reorganize the data so that we average measurements accross SOAs, oddballs and subjects
RR.stats <- RR %>% 
  group_by(oddballtype,subject) %>% 
  dplyr::summarize(relativerecall.mean = mean(relativerecall))

wilcox.test(relativerecall.mean~oddballtype, data=RR.stats, paired=TRUE)

#data needs to be ungrouped to be able to use it now 
RR.stats<-ungroup(RR.stats)

RR.stats %>%
  cohens_d(relativerecall.mean~oddballtype, paired=TRUE)

RRplot



```


# Fig. S3 Normalized Recall 
- QQ plots look fine
- Levene's test p>0.05 
- Analyzed data with a RM ANOVA with factors oddballtype x wordposition 
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a

```{r echo=FALSE,warning=FALSE, message=FALSE}
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
recall<-read.csv('normrec_R.csv')
recall<-as.data.frame(recall)

recall$subject<-factor(recall$subject)
recall$oddballtype<-factor(recall$oddballtype)
recall$wordposition<-factor(recall$wordposition)

recallplot<-recall %>%
  group_by(oddballtype,wordposition) %>%
  get_summary_stats(normrec,type='mean_ci')
recallplot <- dplyr::rename(recallplot, c('normrec' = mean))

recall.fig<-ggplot(recallplot, aes(fill=oddballtype, x=wordposition, y=normrec))+
  geom_bar(position='dodge', stat='identity')+
  geom_errorbar(aes(x=wordposition, ymin=normrec-ci, ymax=normrec+ci), width=0.4, color='wheat4',
                size=0.5, position=position_dodge(0.9), stat='identity')+ 
  geom_jitter(data=recall,aes(color=oddballtype, x=wordposition, y=normrec),    position=position_jitterdodge(dodge.width=0.9), show.legend=FALSE, alpha=0.2)+
  guides(col = FALSE)+
  scale_color_manual(values=c('orchid', 'deepskyblue'))+
  scale_fill_manual(values=c('thistle1','lightblue1'), labels=c('Emotional','Perceptual'), name='Oddball List Type')+
  scale_x_discrete(
    labels = c("Odd-2", "Odd-1", "Odd","Odd+1")
  )+
  #ggtitle('Normalized Recall')+
  labs(x='Word Position', y='Normalized Recall (- control)')+
  theme_classic()

#recall.fig


#Create QQ plot for each cell of design
recall.QQ<-ggqqplot(recall,'normrec',ggtheme=theme_bw())+
  facet_grid(oddballtype~wordposition, labeller='label_both')
recall.QQ #looks fine

levene.recall<-levene_test(normrec~oddballtype*wordposition, data=recall)
levene.recall #meets homogeneity of variances 

recall.aov<-anova_test(
  data=recall,dv=normrec,wid=subject,
  within=c(oddballtype,wordposition)
)
recall.aov
get_anova_table(recall.aov)

#Post-hoc tests 
<<<<<<< HEAD
wp.data<-aggregate(x = recall$normrec, by = list(wordposition=recall$wordposition, subject=recall$subject), FUN = "mean")

WordPosition.pwc<-wp.data %>%
  pairwise_t_test(x~wordposition, paired=TRUE, p.adjust.method='fdr') #%>%
WordPosition.pwc  

wp.data %>%
  cohens_d(x~wordposition, paired=TRUE)

#Interaction oddballtype x word position
=======
WordPosition.pwc<-recall %>%
  #group_by(oddballtype)%>%
  pairwise_t_test(normrec~wordposition, paired=TRUE, p.adjust.method='fdr') #%>%
  #select(-df,-statistic) #remove details 
WordPosition.pwc  

recall %>%
  cohens_d(normrec~wordposition, paired=TRUE)

#Interaction oddballtype x word position

>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a
WordPositionxOdd.pwc<-recall %>%
  group_by(wordposition)%>%
  pairwise_t_test(normrec~oddballtype, paired=TRUE, p.adjust.method='fdr')# %>%
  #select(-df,-statistic) #remove details 
WordPositionxOdd.pwc

recall %>%
  group_by(wordposition) %>%
  cohens_d(normrec~oddballtype, paired=TRUE)

## Add p values to graph 
WordPosition.pwc <- WordPosition.pwc %>% add_xy_position(x = "wordposition")

WordPositionxOdd.pwc <- WordPositionxOdd.pwc %>% add_xy_position(x = "wordposition")

recall.fig+
  stat_pvalue_manual(WordPositionxOdd.pwc, label='{p.adj.signif}', inherit.aes=FALSE, hide.ns=TRUE, tip.length=0, bracket.nudge.y=-0.7)+
<<<<<<< HEAD
  stat_pvalue_manual(WordPosition.pwc, label='{p.adj.signif}', inherit.aes=FALSE, hide.ns=TRUE, tip.length =0, bracket.nudge.y=-0.1)


#Check whether e and p oddballs were better recalled than control words. 
setwd("/Users/albaperis/Desktop/Alba/PhD UPM /Von Restroff WP3/Paper_github/Odd_SOA_CRP/Raw_Results")
oddVcont<-read.csv('v1final_recall_AP.csv')
oddVcont<-as.data.frame(oddVcont)

oddVcont$Subject<-as.factor(oddVcont$Subject)

names(oddVcont)[2] <- "em2"
names(oddVcont)[3] <- "em1"
names(oddVcont)[4] <- "e"
names(oddVcont)[5] <- "ep1"
names(oddVcont)[6] <- "pm2"
names(oddVcont)[7] <- "pm1"
names(oddVcont)[8] <- "p"
names(oddVcont)[9] <- "pp1"
names(oddVcont)[10] <- "ce"
names(oddVcont)[11] <- "cp"

oddVcont<-oddVcont[,c('Subject','em1','ce')]
oddVcont.long<-gather(oddVcont, position, recall, em1:ce, factor_key=TRUE)
#Run a t-test to see whether E-1 items were differently recalled than E control 

Em1.v.EC<-oddVcont.long %>%
  pairwise_t_test(recall~position, paired=TRUE)

oddVcont.long %>%
  cohens_d(recall~position, paired=TRUE)


```

# Fig. S3 E-1, lag+1 correlation 
=======
  stat_pvalue_manual(WordPosition.pwc, label='{p.adj.signif}', inherit.aes=FALSE, hide.ns=TRUE, tip.length =0, bracket.nudge.y=-0.42)
```

# Fig. S4 E-1, lag+1 correlation 
>>>>>>> db7cbadf3ebdf9f20dbcecedff02b127e8e6490a

```{r echo=FALSE, warning=FALSE, message=FALSE}
em1_corr<-as.data.frame(subset(recall, oddballtype=='E' & wordposition=='m1'))
lag_corr<-as.data.frame(subset(TFCRP, oddballtype=='E' & transition=='from' & direction=='Forwards' & wordposition=='1'))

corrplot<-as.data.frame(cbind(em1_corr$normrec,lag_corr$CRP))

corrplt<-ggplot(corrplot, aes(x=V1, y=V2))+
  geom_point(shape=18, color='darksalmon')+
  geom_smooth(method=lm, se=FALSE, color='lightskyblue2')+
  ggtitle('Correlation of E-1 normalized recall and transitions from E Odd (lag +1)')+
  ylab('Lag +1 transitions from E Odd')+
  xlab('E-1 Normalized Recall')+
  theme_classic()

corrplt

cor.test(corrplot$V1, corrplot$V2,  method = "spearman", use = "complete.obs")
```
